
% \bibliographystyle{plain}
\bibliographystyle{GBT7714-2005NLang_Upp}
% \bibliography{chap/references}
%& This .bbl file has been processed by fixbbl!
%& This .bbl file has been processed by fixbbl!
\begin{thebibliography}{148}
%\addtolength{\itemsep}{-1.5 em}
\setlength{\itemsep}{-0.5pt}  % 缩小参考文献间的垂直间距
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
\providecommand{\doi}[1]{doi: #1}\else
\providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

{\wuhaozi \songti
\baselineskip=22pt

% chapter 1
\bibitem{Mattyus-Fine-Grained}
Mattyus G, Wang S, Fidler S, et al. HD Maps: Fine-Grained Road Segmentation by Parsing Ground and Aerial Images[C]// Computer Vision and Pattern Recognition. IEEE, 2016:3611-3619.
\bibitem{Wegner-Higher-Order}
Wegner J D, Montoya-Zegarra J A, Schindler K. A Higher-Order CRF Model for Road Network Extraction[C]// Computer Vision and Pattern Recognition. IEEE, 2013:1698-1705.
\bibitem{Lin-Road-detection}
Lin Y, Saripalli S. Road detection from aerial imagery[C]// IEEE International Conference on Robotics and Automation. IEEE, 2012:3588-3593.
\bibitem{wei-gaofen}
魏宇峰. 高分辨率遥感影像道路信息提取关键技术研究与实现[D]. 北京理工大学, 2010.
\bibitem{wang-yaogan}
汪夕明, 遥感影像道路提取方法研究与实现[D], 北京, 清华大学, 2011.
\bibitem{Xia-Road}
Xia W, Hongmei T, Yang Y等. Study on Road Extraction Method in Remote Sensing Image[A]. 2012 International Conference on Industrial Control and Electronics Engineering (ICICEE)[C]. 2012: 1578C1580.
\bibitem{wuchangchagn-multicore}
Wu C, Agarwal S, Curless B, et al. Multicore bundle adjustment[C] Computer Vision and Pattern Recognition (CVPR), 2011 IEEE Conference on. IEEE, 2011: 3057-3064.
\bibitem{wuchangchang-linear-time}
Wu C. Towards linear-time incremental structure from motion[C] 3DTV-Conference, 2013 International Conference on. IEEE, 2013: 127-134.
\bibitem{Snavely-Building}
Agarwal S, Furukawa Y, Snavely N, et al. Building rome in a day[J]. Communications of the ACM, 2011, 54(10): 105-112.
\bibitem{Snavely-Photo}
Snavely N, Seitz S M, Szeliski R. Photo tourism: exploring photo collections in 3D[C]//ACM transactions on graphics (TOG). ACM, 2006, 25(3): 835-846.
\bibitem{Diosi-Interactive}
Diosi A, Taylor G, Kleeman L. Interactive SLAM using laser and advanced sonar[C]//Robotics and Automation, 2005. ICRA 2005. Proceedings of the 2005 IEEE International Conference on. IEEE, 2005: 1103-1108.

\bibitem{Cole-laser}
Cole D M, Newman P M. Using laser range data for 3D SLAM in outdoor environments[C]//Robotics and Automation, 2006. ICRA 2006. Proceedings 2006 IEEE International Conference on. IEEE, 2006: 1556-1563.

\bibitem{Leonard-concurrent}
Leonard J J. Large-scale concurrent mapping and localization[C] Proceedings of SPIE. 2000, 4196: 370-376.
\bibitem{yangxianghong-wurenji}
杨祥红, 王希彬. 无人机主动 SLAM 技术研究[J]. 系统仿真技术, 2016 (2016 年 04): 283-287.
\bibitem{mayuelong-danmu}
马跃龙, 赵勇, 曹雪峰. 一种基于单目 SLAM 的无人机序列图像拼接方法[J]. 系统仿真学报, 2016 (2016 年 10): 2349-2355.
\bibitem{mengshan-danmu}
蒙山, 唐文名. 单目 SLAM 直线匹配增强平面发现方法[J]. 2017.

\bibitem{chenhanxin-wuren}
陈含欣. 无人机视觉特征提取及同步定位与地图构建方法研究[D].南京航空航天大学,2016.

\bibitem{liuyang-sanwei}
刘洋, 章卫国, 李广文, 等. 一种三维环境中的无人机多路径规划方法[J]. 西北工业大学学报, 2014, 32(3): 412-416.
\bibitem{xiebin-weizhihuanjing}
谢斌, 张开石, 潘华东, 等. 未知环境中无人机适航地图构建与地面目标跟踪[J]. 浙江大学学报: 工学版, 2010 (1): 118-123.
\bibitem{zhirong-dongtai}
邹智荣. 动态环境下自主车同时定位与建图研究[D]. 中南大学, 2012.
\bibitem{zhangyi-wuren}
张毅, 尹亮. 无人车自主导航的环境建图技术[J]. 兵工学报, 2014 (S1): 32-37.
\bibitem{duanfeixu-wuren}
段华旭, 闫飞, 庄严, 等. 无人车基于双目视觉的同时定位与地图构建[J]. 华中科技大学学报: 自然科学版, 2015 (S1): 319-323.
\bibitem{qiufan-semantic}
Fan Q, Yi Y, Hao L, et al. Semantic motion segmentation for urban dynamic scene understanding[C]//Automation Science and Engineering (CASE), 2016 IEEE International Conference on. IEEE, 2016: 497-502.
\bibitem{liyu-jiguagn}
李玉. 基于3D激光点云的无人车城市环境SLAM问题研究[D]. 北京理工大学, 2016.

\bibitem{songxiaohu-OSM}
宋晓虎, 朱纪洪. 基于OpenStreetMap和90 m SRTM的地面站导航电子地图实现[J]. 地球信息科学学报, 2017, 19(7):901-908.

\bibitem{xuqian-wuren}
许谦. 基于无人车环境感知信息的GIS动态更新算法研究[D]. 北京理工大学, 2015.

\bibitem{Mur-Artal-ORB-SLAM}
Mur-Artal R, Montiel J M M, Tardos J D. ORB-SLAM: a versatile and accurate monocular SLAM system[J]. IEEE Transactions on Robotics, 2015, 31(5): 1147-1163.

\bibitem{Engel-LSD-SLAM}
Engel J, Schops T, Cremers D. LSD-SLAM: Large-scale direct monocular SLAM[C] European Conference on Computer Vision. Springer, Cham, 2014: 834-849.

\bibitem{Zhang-LOAM}
Zhang J, Singh S. LOAM: Lidar Odometry and Mapping in Real-time[C]//Robotics: Science and Systems. 2014, 2.

\bibitem{Carrivick-Structure-from-Motion}
Carrivick J L, Smith M W, Quincey D J. Structure from Motion in the Geosciences[M]. John Wiley \& Sons, 2016.

\bibitem{Jianhua-Automated}
Jianhua Wang, Qiming Qin, Xiucheng Yang, Jun Wang, Xin Ye, Xuebin Qin. Automated road extraction from multi-resolution images using spectral information and texture[J]. IEEE Geoscience and Remote Sensing Symposium. 2014. 533-536.
% chapter2-last
\bibitem{Mattyus-Enhancing-road-maps}
Mattyus G, Wang S, Fidler S, et al. Enhancing Road Maps by Parsing Aerial Images Around the World[C] IEEE International Conference on Computer Vision. IEEE, 2015:1689-1697.

\bibitem{Lowe-DistinctiveImageFeatures}
Lowe D G, Lowe D G. Distinctive Image Features from Scale-Invariant Keypoints[J]. International Journal of Computer Vision, 2004, 60(2):91-110.

\bibitem{Bay-Speeded-UpRobustFeatures}
Bay H, Ess A, Tuytelaars T, et al. Speeded-Up Robust Features (SURF)[J]. Computer Vision \& Image Understanding, 2008, 110(3):346-359.

\bibitem{Rublee-ORB:Anefficient}
Rublee E, Rabaud V, Konolige K, et al. ORB: An efficient alternative to SIFT or SURF[C] IEEE International Conference on Computer Vision. IEEE, 2012:2564-2571.

\bibitem{slam14}
高翔, 张涛等, 视觉SLAM十四讲：从理论到实践[B] 电子工业出版社, 2017-3:138

\bibitem{Rosten-FAST}
Rosten E, Drummond T. Machine learning for high-speed corner detection[J]. Computer VisionCECCV 2006, 2006: 430-443.

\bibitem{Harris-corner}
Harris C, Stephens M. A combined corner and edge detector[C] Alvey vision conference. 1988, 15(50): 10.5244.

\bibitem{Lindeberg-Feature detection}
Lindeberg, T.: Feature detection with automatic scale selection. Int. J. Comput. Vis. 30(2),
79C116 (1998)

\bibitem{Lowe-ObjectRecognition}
Lowe D G. Object Recognition from Local Scale-Invariant Features[C]  iccv. IEEE Computer Society, 1999:1150.

\bibitem{Richard-MultipleView}
Multiple View Geometry in Computer Vision Second Edition, Richard Hartley and Andrew Zisserman, Cambridge University Press, March 2004:105

\bibitem{Hartley-MultipleView}
Hartley R, Zisserman A. Multiple view geometry in computer vision[J]. Kybernetes, 2003, 30(9/10):1865 - 1872.
}

\bibitem{Heckbert-polygonal}
P. S. Heckbert and M. Garl, “Survey of polygonal surface simplification
algorithms,” 1997.

\bibitem{Choi-Topological}
C.-H. Choi, J.-B. Song, W. Chung, and M. Kim, Topological map building based on thinning and its application to localization, in Intelligent
Robots and Systems, 2002. IEEE/RSJ International Conference on, vol. 1. IEEE, 2002, pp. 552C557.

\bibitem{Shen-Accurate}
Shen S. Accurate multiple view 3D reconstruction using patch-based stereo for large-scale scenes.[J]. IEEE Transactions on Image Processing A Publication of the IEEE Signal Processing Society, 2013, 22(5):1901.

\bibitem{Furukawa-Accurate}
Furukawa Y, Ponce J. Accurate, Dense, and Robust Multiview Stereopsis[J]. IEEE Transactions on Pattern Analysis \& Machine Intelligence, 2010, 32(8):1362-1376.

\bibitem{Bleyer-PatchMatch}
Bleyer M, Rhemann C, Rother C. PatchMatch Stereo - Stereo Matching with Slanted Support Windows[C]// British Machine Vision Conference. 2011:14.1-14.11.

\bibitem{wu-jisuanji}
吴福朝. 计算机视觉中的数学方法[M]. 科学出版社, 2008.

\bibitem{Turner-Automated}
Turner D, Lucieer A, Watson C. An Automated Technique for Generating Georectified Mosaics from Ultra-High Resolution Unmanned Aerial Vehicle (UAV) Imagery, Based on Structure from Motion (SfM) Point Clouds[J]. Remote Sensing, 2012, 4(5):1392-1410.

\end{thebibliography}
